Interpretable Neural Networks using EAGGA

### 2025-03-15 paper/main.tex
NAS

@@

@@

\subsection{Neural Architecture Search (NAS)}
- approaches specifically for NN HPO due to flexible structure of NNs and thus very large search space (each layer can have different \# nodes, different activations, for CNN different pooling, etc. operations)
- we don't employ NAS for our extension as research focusses on the NLP and image domains, % TODO: find some more references
  whose datasets exhibit strong correlation amongst features (i.e. tokens or pixels, respectively), an effect that is much weaker for tabular data \citep[p. 7499]{Borisov_2024}
- at least want to give a little outline on most notable approaches
  * \textbf{cell search space}
    - modularise NN architecture into cells, NN as chain-structure of those
    - cell = basic building block, fixed component of an NN
      * e.g. linear layer with specific \# of neurons in feedforward
      * or convolutional / pooling / etc layer for CNN
    - then optimise sequential placement of the cells as HPO problem
      * e.g. via random search or BO
      * \citet[p. 3]{zoph2017neuralarchitecturesearchreinforcement} + \citet[pp. 2-4]{Zoph_2018_CVPR} use RNN to recursively optimise HPs of a cell given already determined
        previous cells (+ HPs of current cell), which is trained via RL with the different HPs the RNN predicts being the actions and performance on held-out data being reward
    - \citep[chap. 3.2]{elsken_neural_2019}
  * \textbf{one-shot model}
    - trains one overall ``fabric'' comprising all architectures of search space
    - visualisation as DAG, nodes are layers, edges in-between are operations on a layer's values
    - each path through DAG (from input to output node) represents one architecture of search space -> train entire DAG, then pick optimal path (architecture)
    - pro: very efficient training, individual architectures share operations along edges they share, training one-shot model trains all subsumed models (more expensive
      than training a single model but less expensive than trying out all configurations included in the fabric)
    - \citep[pp. 1-2, p.8]{saxena2017convolutionalneuralfabrics}
    % don't necessarily talk about co-adaptation problem

>>>>

\begin{equation}  % TODO: take out

@@

\begin{equation}  % TODO: make inline or provide further information

@@

\subsection{Neural Architecture Search}
A special case of HPO is Neural Architecture Search (NAS). Because of the flexibility of neural network architectures (number of hidden layers, strength of dropout,
each layer can have a different numer of neurons, each layer can have a different activation function, etc.), traditional HPO methods cannot efficiently explore the
entire space.
In our extension of the EAGGA approach we don't employ NAS as research focusses on the NLP and image domains, % TODO: find some more references
where features (i.e. tokens or pixels, respectively) exhibit strong correlation amongst themselves, which is usually not the case for tabular data \citep[p. 7499]{Borisov_2024}.
Still, we want to outline two notable approaches for neural architecture search in this paper, one of which are \textbf{cell search spcaces}.
These modularise an NN into a chain-structure of cells, where each cell is a basic building block of the respective architecture. For regular feedforwad neural networks,
this could be a linear layer of fixed size and with a specific activation function,
for CNNs this could be a specific convolutional operation or pooling function, for instance.
Instead of tuning every hyperparameter, the sequential placement of the cells is then optimzed during NAS, e.g. via random search or Bayesian
Optimization. \citep[chap. 3.2]{elsken_neural_2019}
\\
Treating a neural network as a sequence of cells instead of one fixed entity further allows exploiting this structure with special sequential optimization techniques.
\citet[p. 3]{zoph2017neuralarchitecturesearchreinforcement} and \citet[pp. 2-4]{Zoph_2018_CVPR} propose a cell search method using RNNs and reinforcement learning.
The cells in their approach are not fixed, but have hyperparameters themselves, such as the filter size and the stride size of a convolutional layer.
These hyperparameters are then predicted sequentially, given all the already predicted hyperparameters of previous layers. The RNN is trained using reinforcement
learning, where the actions are the different values the network can predict for a given hyperparameter and the reward function is the RNN's performance on held-out
validation data.
\\
The second approach to NAS is the \textbf{one-shot model}, which trains a ``fabric'', which can be understood as a DAG comprising all architectures of a given
search space. Each path through the DAG is one specific network architecture, where the nodes represent a layer of neurons and the edges in-between are operations
on the layers' values. The entire DAG has one designated input and one output node.
It is then trained just like a regular NN, after which the optimal path, i.e. network architecture, is selected from the fabric.
This has the advantage of, albeit being slower than training a single model, being far more efficient and less expensive than training all architectures encoded
in the fabric. \citep[pp. 1-2, p.8]{saxena2017convolutionalneuralfabrics}
% don't necessarily talk about co-adaptation problem
